---
title: "ReportAssignment"
output:  md_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Peer-graded Assignment: Course Project 1

## Code for reading in the dataset and/or processing the data

```{r}
echo = TRUE
URL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
temp <- tempfile()
download.file(URL,temp)
data <- read.csv(unz(temp, "activity.csv"))
unlink(temp)
```

## Histogram of the total number of steps taken each day

```{r  echo=TRUE}
Sum1 <- tapply(data$steps, data$date, sum, na.rm=TRUE)
hist(Sum1, xlab = "Total number of steps per day", main = "histogram of steps per day")
```

## Mean and median number of steps taken each day


```{r  echo=TRUE}
Mean1 <- mean(Sum1)
Mean1
Median1 <- median(Sum1)
Median1
```

## Time series plot of the average number of steps taken


```{r  echo=TRUE}
AvgStepInterval <- tapply(data$steps, data$interval, mean, na.rm=T)

plot(AvgStepInterval ~ unique(data$interval), type="l", xlab = "Intervals")
```

## The 5-minute interval that, on average, contains the maximum number of steps


```{r  echo=TRUE}
AvgStepInterval[which.max(AvgStepInterval)]
```

## Code to describe and show a strategy for inputing missing data


```{r  echo=TRUE}
sum(is.na(data))

ASI <- as.data.frame(AvgStepInterval)
ASI <-tibble::rownames_to_column(ASI, "test") 

New <- data

for (i in unique(New$interval)) {
  New$steps[is.na(New$steps) & New$interval == i] <- round(mean(New$steps[New$interval == i], na.rm = T))
}

```

## Histogram of the total number of steps taken each day after missing values are imputed


```{r  echo=TRUE}
Sum2 <- tapply(New$steps, New$date, sum)
hist(Sum2, xlab = "Total number of steps per day", main = "histogram of steps per day")
```

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends


```{r  echo=TRUE}
date <- as.Date(New$date)
weekdayType <- ifelse(weekdays(date) %in% c("Satuday", "Sunday"),"weekend", "weekday")

New <- cbind(New,weekdayType)

StepsWeekday <- aggregate(steps ~ interval+weekdayType, data = New, FUN = mean)


library(ggplot2)
ggplot(StepsWeekday, aes(x = interval, y = steps)) + 
  geom_line(col = "red", size = 1) + 
  facet_wrap(~ weekdayType, nrow=2, ncol=1) + 
  labs(x = "Interval", y = "Number of Steps")
```

## All of the R code needed to reproduce the results (numbers, plots, etc.) in the report


```{r  echo=TRUE}
URL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
temp <- tempfile()
download.file(URL,temp)
data <- read.csv(unz(temp, "activity.csv"))
unlink(temp)


Sum1 <- tapply(data$steps, data$date, sum, na.rm=TRUE)
hist(Sum1, xlab = "Total number of steps per day", main = "histogram of steps per day")

Mean1 <- mean(Sum1)
Mean1
Median1 <- median(Sum1)
Median1

AvgStepInterval <- tapply(data$steps, data$interval, mean, na.rm=T)

plot(AvgStepInterval ~ unique(data$interval), type="l", xlab = "Intervals")

AvgStepInterval[which.max(AvgStepInterval)]

sum(is.na(data))

ASI <- as.data.frame(AvgStepInterval)
ASI <-tibble::rownames_to_column(ASI, "test") 

New <- data

for (i in unique(New$interval)) {
  New$steps[is.na(New$steps) & New$interval == i] <- round(mean(New$steps[New$interval == i], na.rm = T))
}

Sum2 <- tapply(New$steps, New$date, sum)
hist(Sum2, xlab = "Total number of steps per day", main = "histogram of steps per day")

Mean2 <- mean(Sum2)
Mean2
Median2 <- median(Sum2)
Median2

Mean2 - Mean1
Median2 - Median1

date <- as.Date(New$date)
weekdayType <- ifelse(weekdays(date) %in% c("Satuday", "Sunday"),"weekend", "weekday")

New <- cbind(New,weekdayType)

StepsWeekday <- aggregate(steps ~ interval+weekdayType, data = New, FUN = mean)


library(ggplot2)
ggplot(StepsWeekday, aes(x = interval, y = steps)) + 
  geom_line(col = "red", size = 1) + 
  facet_wrap(~ weekdayType, nrow=2, ncol=1) + 
  labs(x = "Interval", y = "Number of Steps")

```

